Meta-analysis Manuscript Wrangling

### 2021-07-05 shared analysis files /manuscript_datavis_22jun21.Rmd
additional figure drafts and stats calcs for heterogeneity

## Non-linear averaging model with all modifiers
```{r, echo = FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

@@

>>>>

## Non-linear averaging model with all modifiers
```{r, echo = FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model

pacman::p_load(esc, dmetar)
summary(full_var_model)
convert_z2r(1.3702) #r=0.8787378
var.comp(full_var_model)

summary(acclimation_model)
convert_z2r(6.0093) #r=0.9999879
```

@@

```{r, echo=FALSE}
mean_temp_acclim <- normalized_acclim %>%
  group_by(mean_temp_reared, flux_range) %>%
  summarise(yi=mean(yi), 
            vi=mean(vi))

mean_var<-normalized_var %>%
  group_by(mean_temp_constant, flux_range) %>%
  summarise(yi=mean(yi), 
            vi=mean(vi))
```

```{r, echo=FALSE}
ggplot(normalized_acclim, aes(y=yi, x=mean_temp_reared, fill=flux_range))+
  geom_line(y=0, linetype = "dashed")+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.7, height = 0.7)+
  geom_errorbar(data=mean_temp_acclim, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_point(data = mean_temp_acclim, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Acclimation and fluctuation range")

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=mean_temp_constant))+
  geom_jitter(alpha = 0.5, pch=21,size=1)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and mean temperature")
